Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-19 prop_letter.tex
prop_letter.tex \paragraph{Quantum Interval-valued Probability Measures (\emph{IVPMs})} Updating...

To formalize the idea of finite precision measurement, we next introduce 
the notion of quantum IVPM~$\bar{\mu}$. The latter replaces 
the infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$ of
intervals. Since the intervals $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$ 
should be included in $\mathscr{I}$, and arithmetic operations on intervals satisfy
\begin{subequations}\label{eq:interval-operations}
\begin{eqnarray}
 &  & \left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right], \textrm{ and}\\
 &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}] ,
\end{eqnarray}
\end{subequations}
$\bar{\mu}:\events\rightarrow\mathscr{I}$ is defined by the axioms:
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
$P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
condition that provides only a bound and not an equivalence as in
Eq. \eqref{eq:QuantumProbability-Addition}. For example, if we consider
$\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
$\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
\[
\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
\]

It is easy to establish that quantum IVPMs generalize conventional
quantum probability measures and classical IVPMs. In particular, any
quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
can be recast as an interval-valued measure~$\iota_{\infty}\circ\mu:\events\rightarrow\mathscr{I}_{\infty}$,
where $\circ$ denotes function composition, $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. In another
word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$ are just the
same as quantum real-valued probability measures where Gleason's theorem
can apply.

More interesting examples comes when we focus on only three intervals
$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
it provides no information. Then,
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
is a quantum IVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in question.

@@

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.

>>>>

To formalize the idea of finite precision measurement, we next introduce 
the notion of quantum IVPM~$\bar{\mu}$. The latter replaces 
the infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$ of
intervals. Since the intervals $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$ 
should be included in $\mathscr{I}$, and arithmetic operations on intervals satisfy
\begin{subequations}\label{eq:interval-operations}
\begin{eqnarray}
 &  & \left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right], \textrm{ and}\\
 &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}] ,
\end{eqnarray}
\end{subequations}
$\bar{\mu}:\events\rightarrow\mathscr{I}$ is defined by the axioms:
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
$P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
condition that provides only a bound and not an equivalence as in
Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
$\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
$\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
\[
\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
\]

Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum interval-valued probability measure, i.e.,
given observations done with finite resources. Since the probabilities
are intervals, it is intuitive to say a state~$\rho$ is consistent
with $\bar{\mu}$ on a projector~$P$ if 
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)\textrm{ .}
\end{equation}

Since our measurement is fuzzy, generally there are more than one
state consistent with a particular quantum IVPM. For example, consider
three intervals $\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
it provides no information. Then,
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
is a quantum IVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in question,
and any state is consistent with $\bar{\mu}_{1}$ on any projectors.

In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum probability measure can be recast as an interval-valued
one. For $d\ge3$, the question reduces to Gleason's theorem which
states that for any quantum IVPM~$\bar{\mu}$, there is an unique
state can be consistent with $\bar{\mu}$ on every projector.

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
However, before dive into the Kochen-Specker theorem, it is better
to understand how to define expectation value of an observable with
quantum IVPMs.

@@
